method

### 2021-12-06 06_Paper/ER-ED/method.Rmd
corrected loop

# new empty frame to store files into
data_ER = data.frame(ID = character(), block = character(), arousal = double(), effort = double())

@@

>>>>

# new empty frame to store files into
data_ER = data.frame(ID = character(), block = character(), arousal = double(), effort = double(), trigger = double(), trigger_reg = double())

@@

rownames(data_ER) = 1:nrow(data_ER)

# loop to store trigger in one column

for (i in 1:nrow(data_ER)) {
  if (is.na(data_ER$trigger[i])) {
    data_ER$trigger[i] = data_ER$trigger_reg[i]
  }

  if (is.na(data_ER$trigger[i])) {
    data_ER$trigger[i] = 26
  }
}

# delete old column

data_ER$trigger_reg = NULL

# loop to correct block indicator

for (i in 1:nrow(data_ER)) {

  if (data_ER$trigger[i] == 21) {

    data_ER$block[i] = "view_neu"

  } else if (data_ER$trigger[i] == 22) {

    data_ER$block[i] = "view_neg"

  } else if (data_ER$trigger[i] == 23 ) {

    data_ER$block[i] = "distraction"

  } else if (data_ER$trigger[i] == 24 ) {

    data_ER$block[i] = "distancing"

  } else if (data_ER$trigge[i] == 25 ) {

    data_ER$block[i] = "suppression"

  } else if (data_ER$trigger[i] == 25) {

    data_ER$block[i] = "choice"
  }
}
